---
title: "Summary of Recodes"
author: "Simon J. Kiss, Matthew J. Arp and Scott Lu"
date: "09/03/2021"
output: word_document
---

```{r setup, include=FALSE, echo=F}
knitr::opts_chunk$set(echo = TRUE, message=F, warning=T, echo=F, cache=T)

```


```{r load-data, results="hide", eval=T}
library(here)
source(here('R_Scripts', '2_data_preparation.R'))
```

## Introduction

This document tracks and summarizes basic data wrangling and recodes conducted at LISPOP for the 2021 Canadian Public Health Workforce and General Population Survey. The purpose of this document is to facilitate multi-institutional collaboration. LISPOP staff will take on the task of basic variable recodes and export data files for analysis by project researchers so that they can dedicate their attention to substantive analyses. 

## Scientific Literacy Questions

We have recoded variables Q14_1, Q14_2, Q14_3 and Q14_4 into variables `know1`, `know2`, 'know3' and `know4` such that respondents were coded 1 if they were correct and 0 if they were incorrect. 

If Q14_1 = 1 or 2 (Definitely or Probably false), it is correct
"Ordinary tomatoes do not contain genes, while genetically modified tomatoes do."


If Q14_2 = 1 or 2 (Definitely or Probably false), it is correct
"Antibiotics kill viruses as well as bacteria."

```{r eval=F, echo=FALSE}
      know1=case_when(
      Q14_1<3 ~ 1,
      Q14_1>2 ~ 0,
      TRUE ~ 0

```
```{r eval=F, echo=FALSE}
      know1=case_when(
      Q14_2<3 ~ 1,
      Q14_2>2 ~ 0,
      TRUE ~ 0

```

If Q14_3 = 3 or 4 (Definitely or Probably true), it is correct
"The cloning of living things produces genetically identical copies."

If Q14_4 = 3 or 4 (Definitely or Probably true), it is correct
"All plants and animals have DNA."


```{r eval=F, echo=FALSE}
know3=case_when(
    Q14_3>2 ~ 1,
    Q14_3<3 ~ 0,
    TRUE ~ 0

```
```{r eval=F, echo=FALSE}
know3=case_when(
    Q14_4>2 ~ 1,
    Q14_4<3 ~ 0,
    TRUE ~ 0

```


```{r compare-scientific-literacy, results='hide', echo=F}

full %>% 
  select(Q14_1:Q14_4, starts_with('know')) %>% 
  as_factor() 
```


## Cognitive Reflection test Questions 
We have recoded variables Q18_1, Q19_1, Q20_1 and Q21_1 into variables `crt1`, `crt2` etc.such that respondents were coded 1 if they got the correct response and 0 if they were incorrect. 

CRT Question Q18_1 coded 1 when answer (X) is a variation of "Second Place"
"If you’re running a race and you pass the person in second place, what place are you in?"

CRT Question Q19_1 coded 1 when answer (X) is a variation of "Eight"
"A farmer had 15 sheep and all but 8 died. How many are left?"

CRT Question Q20_1 coded 1 when answer (X) is a variation of "Emily"
"Emily’s father has three daughters. The first two are named April and May. What is the third daughter’s name?"

CRT Question Q21_1 coded 1 when answer (X) is a variation of "None"
"How many cubic feet of dirt are there in a hole that is 3’ deep x 3’ wide x 3’ long?"



```{r compare-crt, echo=F}
full %>% 
  select(Q18_1:Q21_1, starts_with('crt')) %>% 
  as_factor() 
```
## Most Important Problem in Public Health 
We have provided more meaningful variable names (e.g. `Obesity`, `Vaccine Hesitancy` , etc. ) and *appended* these to the dataset. The original variables are `Q1_1` through `Q1_9`. In addition, because respondents were given the option to add `other` open ended responses, we have gone through these and coded these into some meaningful categories. The categories are currently these: 

1 = COVID-19

2 = Public health messaging/gov't handling of COVID

3 = Healthcare (access to care, short supply)

4 = Long term care

5 = Chronic disease (cancer, heart disease)

6 = Mental health

7 = Access to housing and food

8 = Drug abuse

9 = Inequality

10 = Economy

11 = Corrupt gov't

12 = Climate change/environmental

13 = Abortion

14 = Reliance on meat

15 = Domestic abuse

16 = Misinformation

17 = Internet addiction

18 = Don't know


